### 2018-04-11 paper.Rmd
builds, tweaks to refs

keywords          : "keywords"
wordcount         : "X"

@@

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
library(koRpus)
library(png)
library(here)
library(lme4)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

- Sparsely annotated tiers, e.g. phonology (`%pho`) and situation (`%sit`)
<!--- Media links, including timing information AS: we have media timestamps -->
<!--- Compound word markers, indicated with underscores ("green_eggs_and_ham") AS: we have this -->
- Tone direction and stress
- Filled pauses 
- Reformulations, word revision, and phrase revision, e.g. \textlt what did you\textgt [//] how can you see it ?
- paralinguistic material, e.g. [=! cries]

@@

The lexical statistics of language input to children have long been an object of study in child language acquisition research. Frequency counts of words in particular may provide insight into the cognitive, conceptual, and linguistic experience of a young child [see e.g., @ambridge2015 for review]. In this web app, inspired by ChildFreq [@baath2015], we provide users the ability to search for any word spoken by a participant in the CHILDES corpora and track the usage of that word by a child or caregiver over time. Because of the various toggles available to the user that can subset the data, a user may display frequency curves for a single child in the Brown corpus or all Spanish speaking children, if desired. In addition, users can plot frequency curves belonging to caregivers alongside their child for convenient side-by-side comparisons. A single word or multiple words may be entered into the input box.

@@

The syntactic complexity and lexical diversity of children's speech are similarly critical metrics for acquisition researchers [@miller1981,@watkins1995]. There are a number of well-established measures of children's speech that operationalize complexity and diversity. These developmental metrics have many applications in speech-language pathology (SLP), where measures outside of the normal range may be indicative of speech, language, or communication disorders.

@@

```{r color-plot, fig.height = 5, fig.width = 10, fig.cap ="Color frequency as a function of age. Points represent means across transcripts, error bars represent 95% confidence intervals computed by nonparametric bootstrap", cache = TRUE, message = FALSE, warning = FALSE}
ggplot(count_estimates_with_error, aes(x = age_bin, y = empirical_stat, 
                            ymin = ci_lower, ymax = ci_upper,
                            color = color, label = color)) + 
  geom_pointrange(position = position_dodge(.5)) + 
  geom_point() +
  geom_smooth(method = "loess", se = F, span = .5) +
  facet_wrap(~ color, scales = "free_y") + 
  theme_classic(base_size = 14) +
  scale_color_manual(values = graph_colors$graph_color) +
  scale_x_continuous(breaks = seq(12, 60, 12),
                     name = "Age (months)") + 
  scale_y_continuous(name = "Frequency (per million words)") +
  geom_dl(method = list(dl.trans(x=x +.2), "last.qp", cex=1)) + 
  theme(legend.position = "none")
```

>>>>

keywords          : "child language; corpus linguistics; reproducibility; R packages; research software"
wordcount         : "2925"

@@

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
library(koRpus)
library(png)
library(here)
library(lme4)
library(ggthemes)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

- Sparsely annotated tiers, e.g. phonology (`%pho`) and situation (`%sit`)
<!--- Media links, including timing information AS: we have media timestamps -->
<!--- Compound word markers, indicated with underscores ("green_eggs_and_ham") AS: we have this -->
- Tone direction and stress
- Filled pauses 
- Reformulations, word revision, and phrase revision, e.g. \textless what did you\textgreater [//] how can you see it ?
- paralinguistic material, e.g. [=! cries]

@@

The lexical statistics of language input to children have long been an object of study in child language acquisition research. Frequency counts of words in particular may provide insight into the cognitive, conceptual, and linguistic experience of a young child [see e.g., @ambridge2015 for review]. In this web app, inspired by ChildFreq [@baath2010], we provide users the ability to search for any word spoken by a participant in the CHILDES corpora and track the usage of that word by a child or caregiver over time. Because of the various toggles available to the user that can subset the data, a user may display frequency curves for a single child in the Brown corpus or all Spanish speaking children, if desired. In addition, users can plot frequency curves belonging to caregivers alongside their child for convenient side-by-side comparisons. A single word or multiple words may be entered into the input box.

@@

The syntactic complexity and lexical diversity of children's speech are similarly critical metrics for acquisition researchers [@miller1981;@watkins1995]. There are a number of well-established measures of children's speech that operationalize complexity and diversity. These developmental metrics have many applications in speech-language pathology (SLP), where measures outside of the normal range may be indicative of speech, language, or communication disorders.

@@

```{r color-plot, fig.height = 5, fig.width = 10, fig.cap ="Color frequency as a function of age. Points represent means across transcripts, error bars represent 95% confidence intervals computed by nonparametric bootstrap", cache = TRUE, message = FALSE, warning = FALSE}
ggplot(count_estimates_with_error, aes(x = age_bin, y = empirical_stat, 
                            ymin = ci_lower, ymax = ci_upper,
                            color = color, label = color)) + 
  geom_pointrange(position = position_dodge(.5)) + 
  geom_point() +
  geom_smooth(method = "loess", se = F, span = .5) +
  facet_wrap(~ color, scales = "free_y") + 
  theme_few() +
  scale_color_manual(values = graph_colors$graph_color) +
  scale_x_continuous(breaks = seq(12, 60, 12),
                     name = "Age (months)") + 
  scale_y_continuous(name = "Frequency (per million words)") +
  geom_dl(method = list(dl.trans(x=x +.2), "last.qp", cex=1)) + 
  theme(legend.position = "none")
```
